\vspace{1.0cm} \Large \bf Integrating influenza antigenic dynamics with molecular evolution

### 2013-04-04 cover_letter.tex
Address eLife rather than PNAS.

\greetto{Dear Prof.\ Levin,}
\closeline{Sincerely,}

@@

Please find, attached, our manuscript entitled ``Integrating influenza antigenic dynamics with molecular evolution,'' which we would be grateful for your consideration for publication in \textit{Proc Natl Acad Sci USA}.  
We believe that \textit{Proc Natl Acad Sci USA} is an appropriate venue for this work, as it clarifies long-standing questions about the antigenic and evolutionary dynamics of influenza viruses, while simultaneously presenting a major methodological advance in the characterization of antigenic phenotype.

>>>>

\greetto{Dear Editor,}
\closeline{Sincerely,}

@@

Please find, attached, our manuscript entitled ``Integrating influenza antigenic dynamics with molecular evolution,'' which we would be grateful for your consideration for publication in \textit{eLife}.  
We believe that \textit{eLife} is an appropriate venue for this work, as it clarifies long-standing questions about the antigenic and evolutionary dynamics of influenza viruses, while simultaneously presenting a major methodological advance in the characterization of antigenic phenotype.
